%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Teacher Assistant} % Job title
    {Drury University} % Organization
    {Springfield MO, USA} % Location
    {2023 - 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Aided in one Introduction to Computer Science section with no failing students.}
        \item{Guided occasional lectures for exam reviews that improved scores on average a 30\%.}
        \item{Led weekly lab sessions to implement different data structures in Python.}
        \item{Fostered an environment of trust in two separate Computer Science classes with one-to-one sessions with 20\% of students.}
        \item{Implmented automatic grading through GitHub Actions to cut down on grading time by 60\%.}
        \item{Held weekly meetings with faculty to prepare lectures and material for upcoming classes.}
        \end{cvitems}
    }

        %---------------------------------------------------------

    \cventry
    {Computer Science Tutor} % Job title
    {Drury University} % Organization
    {Springfield MO, USA} % Location
    {2022 - 2024} % Date(s)
    {
        \begin{cvitems}
        \item{Carried north of 350 tutoring sessions from 2022 - 2024 focused on Computer Science concepts.}
        \item{Improved by at least one letter the grades of students who frequented tutoring.}
        \item{Explained on a step-by-step basis fundamental algorithms and implementations in Python \& JavaScript with up to 9 students at a time.}
        \item{Empowered Non-Computer Science students in implementing programming concepts to optimize workflows within their respective fields.}
        \item{Collaborated with faculty on a regular basis to prepare explanations for different assignments and tests in all the department classes.}
        \item{Became one of the top learning resources for students who frequented tutoring in the department of Computer Science.}
        \end{cvitems}
    }


\end{cventries}
